#### A

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-3596}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::freq(
    var = year,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_bar(
    col = 'year',
    y_label = 'year'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `number_of_children`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-number-of-children-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = number_of_children,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-number-of-children-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'number_of_children',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-sisvan-cover-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = sisvan_cover,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-sisvan-cover-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'sisvan_cover',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mbepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'mbepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-beipr-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-beipr-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-beipr-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mbepr_beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-beipr-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'mbepr_beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = maper,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'maper',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mpepr-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mpepr-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-mpepr-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = maper_mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-mpepr-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'maper_mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-gdp-per-capita-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = gdp_per_capita,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-gdp-per-capita-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'gdp_per_capita',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-spei-12m-3596 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = spei_12m,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-spei-12m-3596}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = 'spei_12m',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### B

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-6694}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::freq(
    var = year,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_bar(
    col = 'year',
    y_label = 'year'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `number_of_children`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-number-of-children-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = number_of_children,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-number-of-children-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'number_of_children',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-sisvan-cover-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = sisvan_cover,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-sisvan-cover-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'sisvan_cover',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mbepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'mbepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-beipr-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-beipr-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-beipr-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mbepr_beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-beipr-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'mbepr_beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = maper,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'maper',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mpepr-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mpepr-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-mpepr-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = maper_mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-mpepr-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'maper_mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-gdp-per-capita-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = gdp_per_capita,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-gdp-per-capita-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'gdp_per_capita',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-spei-12m-6694 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = spei_12m,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-spei-12m-6694}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = 'spei_12m',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### C

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-2824}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::freq(
    var = year,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_bar(
    col = 'year',
    y_label = 'year'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `number_of_children`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-number-of-children-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = number_of_children,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-number-of-children-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'number_of_children',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-sisvan-cover-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = sisvan_cover,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-sisvan-cover-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'sisvan_cover',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mbepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'mbepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-beipr-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-beipr-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-beipr-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mbepr_beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-beipr-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'mbepr_beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = maper,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'maper',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mpepr-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mpepr-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-mpepr-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = maper_mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-mpepr-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'maper_mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-gdp-per-capita-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = gdp_per_capita,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-gdp-per-capita-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'gdp_per_capita',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-spei-12m-2824 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = spei_12m,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-spei-12m-2824}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = 'spei_12m',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### D

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-8000}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::freq(
    var = year,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_bar(
    col = 'year',
    y_label = 'year'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `number_of_children`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-number-of-children-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = number_of_children,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-number-of-children-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'number_of_children',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-sisvan-cover-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = sisvan_cover,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-sisvan-cover-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'sisvan_cover',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mbepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'mbepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-beipr-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-beipr-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mbepr-beipr-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mbepr_beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mbepr-beipr-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'mbepr_beipr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = maper,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'maper',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-mpepr-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-mpepr-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-maper-mpepr-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = maper_mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-maper-mpepr-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'maper_mpepr',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-gdp-per-capita-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = gdp_per_capita,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-gdp-per-capita-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'gdp_per_capita',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

:::: {.grid}
::: {.g-col-1}
:::

::: {#tbl-var-distribution-stats-spei-12m-8000 .g-col-10}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = spei_12m,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: NA]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {.g-col-1}
:::
::::

::: {#fig-var-distribution-charts-spei-12m-8000}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = 'spei_12m',
    jitter = FALSE
  )
```

[Source: NA]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::
