:::: {.panel-tabset}
#### `year`

::: {#tbl-var-distribution-freqs-year-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::freq(
    var = year,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-7063}
```{r}
#| code-fold: true

data |>
  plot_bar(
    col = 'year',
    y_label = 'year'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

#### `misf`

::: {#tbl-var-distribution-freqs-misf-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::freq(
    var = misf,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `misf` variable.
:::

::: {#fig-var-distribution-charts-misf-7063}
```{r}
#| code-fold: true

data |>
  plot_bar(
    col = 'misf',
    y_label = 'misf'
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `misf` variable.
:::

#### `number_of_children`

::: {#tbl-var-distribution-stats-number-of-children-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = number_of_children,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {#fig-var-distribution-charts-number-of-children-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'number_of_children',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `sisvan_cover`

::: {#tbl-var-distribution-stats-sisvan-cover-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = sisvan_cover,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {#fig-var-distribution-charts-sisvan-cover-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'sisvan_cover',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `mbepr`

::: {#tbl-var-distribution-stats-mbepr-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = mbepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'mbepr',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `beipr`

::: {#tbl-var-distribution-stats-beipr-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `beipr` variable.
:::

::: {#fig-var-distribution-charts-beipr-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'beipr',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `mbepr_beipr`

::: {#tbl-var-distribution-stats-mbepr-beipr-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = mbepr_beipr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-beipr-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'mbepr_beipr',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `maper`

::: {#tbl-var-distribution-stats-maper-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = maper,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper` variable.
:::

::: {#fig-var-distribution-charts-maper-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'maper',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `mpepr`

::: {#tbl-var-distribution-stats-mpepr-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mpepr` variable.
:::

::: {#fig-var-distribution-charts-mpepr-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'mpepr',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `maper_mpepr`

::: {#tbl-var-distribution-stats-maper-mpepr-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = maper_mpepr,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {#fig-var-distribution-charts-maper-mpepr-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'maper_mpepr',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `gdp_per_capita`

::: {#tbl-var-distribution-stats-gdp-per-capita-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = gdp_per_capita,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {#fig-var-distribution-charts-gdp-per-capita-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'gdp_per_capita',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

#### `spei_12m`

::: {#tbl-var-distribution-stats-spei-12m-7063}
```{r}
#| code-fold: true
#| output: asis

data |>
  summarytools::descr(
    var = spei_12m,
    style = 'rmarkdown',
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {#fig-var-distribution-charts-spei-12m-7063}
```{r}
#| code-fold: true

data |>
  plot_dist(
    col = 'spei_12m',
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::
