#### A

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::freq(
    var = year,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_bar(
    col = "year",
    y_label = "year"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `misf`

::: {#tbl-var-distribution-freqs-misf-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::freq(
    var = misf,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `misf` variable.
:::

::: {#fig-var-distribution-charts-misf-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_bar(
    col = "misf",
    y_label = "misf"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `misf` variable.
:::

##### `number_of_children`

::: {#tbl-var-distribution-stats-number-of-children-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = number_of_children,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {#fig-var-distribution-charts-number-of-children-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "number_of_children",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

::: {#tbl-var-distribution-stats-sisvan-cover-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = sisvan_cover,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {#fig-var-distribution-charts-sisvan-cover-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "sisvan_cover",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

::: {#tbl-var-distribution-stats-mbepr-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mbepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "mbepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

::: {#tbl-var-distribution-stats-beipr-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `beipr` variable.
:::

::: {#fig-var-distribution-charts-beipr-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

::: {#tbl-var-distribution-stats-mbepr-beipr-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mbepr_beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-beipr-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "mbepr_beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

::: {#tbl-var-distribution-stats-maper-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = maper,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper` variable.
:::

::: {#fig-var-distribution-charts-maper-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "maper",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

::: {#tbl-var-distribution-stats-mpepr-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mpepr` variable.
:::

::: {#fig-var-distribution-charts-mpepr-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

::: {#tbl-var-distribution-stats-maper-mpepr-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = maper_mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {#fig-var-distribution-charts-maper-mpepr-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "maper_mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gini_index`

::: {#tbl-var-distribution-stats-gini-index-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = gini_index,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gini_index` variable.
:::

::: {#fig-var-distribution-charts-gini-index-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "gini_index",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gini_index` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

::: {#tbl-var-distribution-stats-gdp-per-capita-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = gdp_per_capita,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {#fig-var-distribution-charts-gdp-per-capita-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "gdp_per_capita",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

::: {#tbl-var-distribution-stats-spei-12m-3356}
```{r}
#| code-fold: true
#| output: asis

data_misfs_a |>
  summarytools::descr(
    var = spei_12m,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {#fig-var-distribution-charts-spei-12m-3356}
```{r}
#| code-fold: true

data_misfs_a |>
  plot_dist(
    col = "spei_12m",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### B

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::freq(
    var = year,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_bar(
    col = "year",
    y_label = "year"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `misf`

::: {#tbl-var-distribution-freqs-misf-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::freq(
    var = misf,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `misf` variable.
:::

::: {#fig-var-distribution-charts-misf-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_bar(
    col = "misf",
    y_label = "misf"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `misf` variable.
:::

##### `number_of_children`

::: {#tbl-var-distribution-stats-number-of-children-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = number_of_children,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {#fig-var-distribution-charts-number-of-children-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "number_of_children",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

::: {#tbl-var-distribution-stats-sisvan-cover-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = sisvan_cover,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {#fig-var-distribution-charts-sisvan-cover-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "sisvan_cover",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

::: {#tbl-var-distribution-stats-mbepr-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mbepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "mbepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

::: {#tbl-var-distribution-stats-beipr-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `beipr` variable.
:::

::: {#fig-var-distribution-charts-beipr-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

::: {#tbl-var-distribution-stats-mbepr-beipr-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mbepr_beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-beipr-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "mbepr_beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

::: {#tbl-var-distribution-stats-maper-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = maper,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper` variable.
:::

::: {#fig-var-distribution-charts-maper-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "maper",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

::: {#tbl-var-distribution-stats-mpepr-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mpepr` variable.
:::

::: {#fig-var-distribution-charts-mpepr-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

::: {#tbl-var-distribution-stats-maper-mpepr-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = maper_mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {#fig-var-distribution-charts-maper-mpepr-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "maper_mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gini_index`

::: {#tbl-var-distribution-stats-gini-index-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = gini_index,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gini_index` variable.
:::

::: {#fig-var-distribution-charts-gini-index-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "gini_index",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gini_index` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

::: {#tbl-var-distribution-stats-gdp-per-capita-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = gdp_per_capita,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {#fig-var-distribution-charts-gdp-per-capita-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "gdp_per_capita",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

::: {#tbl-var-distribution-stats-spei-12m-3112}
```{r}
#| code-fold: true
#| output: asis

data_misfs_b |>
  summarytools::descr(
    var = spei_12m,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {#fig-var-distribution-charts-spei-12m-3112}
```{r}
#| code-fold: true

data_misfs_b |>
  plot_dist(
    col = "spei_12m",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### C

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::freq(
    var = year,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_bar(
    col = "year",
    y_label = "year"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `misf`

::: {#tbl-var-distribution-freqs-misf-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::freq(
    var = misf,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `misf` variable.
:::

::: {#fig-var-distribution-charts-misf-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_bar(
    col = "misf",
    y_label = "misf"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `misf` variable.
:::

##### `number_of_children`

::: {#tbl-var-distribution-stats-number-of-children-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = number_of_children,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {#fig-var-distribution-charts-number-of-children-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "number_of_children",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

::: {#tbl-var-distribution-stats-sisvan-cover-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = sisvan_cover,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {#fig-var-distribution-charts-sisvan-cover-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "sisvan_cover",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

::: {#tbl-var-distribution-stats-mbepr-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mbepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "mbepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

::: {#tbl-var-distribution-stats-beipr-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `beipr` variable.
:::

::: {#fig-var-distribution-charts-beipr-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

::: {#tbl-var-distribution-stats-mbepr-beipr-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mbepr_beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-beipr-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "mbepr_beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

::: {#tbl-var-distribution-stats-maper-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = maper,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper` variable.
:::

::: {#fig-var-distribution-charts-maper-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "maper",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

::: {#tbl-var-distribution-stats-mpepr-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mpepr` variable.
:::

::: {#fig-var-distribution-charts-mpepr-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

::: {#tbl-var-distribution-stats-maper-mpepr-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = maper_mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {#fig-var-distribution-charts-maper-mpepr-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "maper_mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gini_index`

::: {#tbl-var-distribution-stats-gini-index-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = gini_index,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gini_index` variable.
:::

::: {#fig-var-distribution-charts-gini-index-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "gini_index",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gini_index` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

::: {#tbl-var-distribution-stats-gdp-per-capita-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = gdp_per_capita,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {#fig-var-distribution-charts-gdp-per-capita-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "gdp_per_capita",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

::: {#tbl-var-distribution-stats-spei-12m-4893}
```{r}
#| code-fold: true
#| output: asis

data_misfs_c |>
  summarytools::descr(
    var = spei_12m,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {#fig-var-distribution-charts-spei-12m-4893}
```{r}
#| code-fold: true

data_misfs_c |>
  plot_dist(
    col = "spei_12m",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::

#### D

:::: {.panel-tabset}
##### `year`

::: {#tbl-var-distribution-freqs-year-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::freq(
    var = year,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `year` variable.
:::

::: {#fig-var-distribution-charts-year-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_bar(
    col = "year",
    y_label = "year"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `year` variable.
:::

##### `misf`

::: {#tbl-var-distribution-freqs-misf-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::freq(
    var = misf,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Frequencies of the `misf` variable.
:::

::: {#fig-var-distribution-charts-misf-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_bar(
    col = "misf",
    y_label = "misf"
  )
```

[Source: Created by the authors.]{.legend}

Bar plot of the `misf` variable.
:::

##### `number_of_children`

::: {#tbl-var-distribution-stats-number-of-children-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = number_of_children,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `number_of_children` variable.
:::

::: {#fig-var-distribution-charts-number-of-children-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "number_of_children",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `number_of_children` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `sisvan_cover`

::: {#tbl-var-distribution-stats-sisvan-cover-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = sisvan_cover,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `sisvan_cover` variable.
:::

::: {#fig-var-distribution-charts-sisvan-cover-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "sisvan_cover",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `sisvan_cover` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr`

::: {#tbl-var-distribution-stats-mbepr-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mbepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "mbepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `beipr`

::: {#tbl-var-distribution-stats-beipr-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `beipr` variable.
:::

::: {#fig-var-distribution-charts-beipr-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mbepr_beipr`

::: {#tbl-var-distribution-stats-mbepr-beipr-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mbepr_beipr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mbepr_beipr` variable.
:::

::: {#fig-var-distribution-charts-mbepr-beipr-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "mbepr_beipr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mbepr_beipr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper`

::: {#tbl-var-distribution-stats-maper-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = maper,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper` variable.
:::

::: {#fig-var-distribution-charts-maper-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "maper",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `mpepr`

::: {#tbl-var-distribution-stats-mpepr-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `mpepr` variable.
:::

::: {#fig-var-distribution-charts-mpepr-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `maper_mpepr`

::: {#tbl-var-distribution-stats-maper-mpepr-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = maper_mpepr,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `maper_mpepr` variable.
:::

::: {#fig-var-distribution-charts-maper-mpepr-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "maper_mpepr",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `maper_mpepr` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gini_index`

::: {#tbl-var-distribution-stats-gini-index-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = gini_index,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gini_index` variable.
:::

::: {#fig-var-distribution-charts-gini-index-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "gini_index",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gini_index` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `gdp_per_capita`

::: {#tbl-var-distribution-stats-gdp-per-capita-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = gdp_per_capita,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `gdp_per_capita` variable.
:::

::: {#fig-var-distribution-charts-gdp-per-capita-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "gdp_per_capita",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `gdp_per_capita` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::

##### `spei_12m`

::: {#tbl-var-distribution-stats-spei-12m-7166}
```{r}
#| code-fold: true
#| output: asis

data_misfs_d |>
  summarytools::descr(
    var = spei_12m,
    style = "rmarkdown",
    plain.ascii = FALSE,
    headings = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Statistics for the `spei_12m` variable.
:::

::: {#fig-var-distribution-charts-spei-12m-7166}
```{r}
#| code-fold: true

data_misfs_d |>
  plot_dist(
    col = "spei_12m",
    jitter = FALSE
  )
```

[Source: Created by the authors.]{.legend}

Histogram of the `spei_12m` variable with a kernel density estimate, a quantile-quantile (Q-Q) plot comparing the variable to the theoretical normal distribution, and a boxplot highlighting outliers in red.
:::
::::
