:::: {.panel-tabset}
#### MBEPR – Very Short Stature for Age (*Muito Baixa Estatura Para a Idade*)

```{r}
mbepr_gam_3 <- mgcv::gam(
  mbepr ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

mbepr_gam_3 |> summary()
```

::: {#tbl-mbepr-gam-3-r2}
```{r}
#| output: asis

mbepr_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mbepr_gam_3` model.
:::

::: {#tbl-mbepr-gam-3-summary-stats}
```{r}
#| output: asis

mbepr_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mbepr_gam_3` model.
:::

::: {#tbl-mbepr-gam-3-coef-stats}
```{r}
#| output: asis

mbepr_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_gam_3` model.
:::

```{r}
mbepr_gam_3 |> mgcv::gam.check()
```

::: {#fig-mbepr-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = mbepr_gam_3,
    type = 3,
    title = 'Very Short Stature for Age versus (MBEPR) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of MBEPR'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `mbepr` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``mbepr_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::

#### BEIPR – Short Stature for Age (*Baixa Estatura Para Idade*)

```{r}
beipr_gam_3 <- mgcv::gam(
  beipr ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

beipr_gam_3 |> summary()
```

::: {#tbl-beipr-gam-3-r2}
```{r}
#| output: asis

beipr_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`beipr_gam_3` model.
:::

::: {#tbl-beipr-gam-3-summary-stats}
```{r}
#| output: asis

beipr_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `beipr_gam_3` model.
:::

::: {#tbl-beipr-gam-3-coef-stats}
```{r}
#| output: asis

beipr_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `beipr_gam_3` model.
:::

```{r}
beipr_gam_3 |> mgcv::gam.check()
```

::: {#fig-beipr-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = beipr_gam_3,
    type = 3,
    title = 'Short Stature for Age (BEIPR) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of BEIPR'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `beipr` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``beipr_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::

#### MBEPR & BEIPR – Very Short/Short Stature for Age (*Muito Baixa/Baixa Estatura Para Idade*)

```{r}
mbepr_beipr_gam_3 <- mgcv::gam(
  mbepr_beipr ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

mbepr_beipr_gam_3 |> summary()
```

::: {#tbl-mbepr-beipr-gam-3-r2}
```{r}
#| output: asis

mbepr_beipr_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mbepr_beipr_gam_3` model.
:::

::: {#tbl-mbepr-beipr-gam-3-summary-stats}
```{r}
#| output: asis

mbepr_beipr_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mbepr_beipr_gam_3` model.
:::

::: {#tbl-mbepr-beipr-gam-3-coef-stats}
```{r}
#| output: asis

mbepr_beipr_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_beipr_gam_3` model.
:::

```{r}
mbepr_beipr_gam_3 |> mgcv::gam.check()
```

::: {#fig-mbepr-beipr-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = mbepr_beipr_gam_3,
    type = 3,
    title = 'Very Short/Short Stature for Age (MBEPR & BEIPR) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of MBEPR & BEIPR'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `mbepr_beipr` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``mbepr_beipr_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::

#### MAPER – Severe Thinness for Height (*Magreza Acentuada Para a Estatura*)

```{r}
maper_gam_3 <- mgcv::gam(
  maper ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

maper_gam_3 |> summary()
```

::: {#tbl-maper-gam-3-r2}
```{r}
#| output: asis

maper_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`maper_gam_3` model.
:::

::: {#tbl-maper-gam-3-summary-stats}
```{r}
#| output: asis

maper_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `maper_gam_3` model.
:::

::: {#tbl-maper-gam-3-coef-stats}
```{r}
#| output: asis

maper_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_gam_3` model.
:::

```{r}
maper_gam_3 |> mgcv::gam.check()
```

::: {#fig-maper-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = maper_gam_3,
    type = 3,
    title = 'Severe Thinness for Height (MAPER) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of MAPER'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `maper` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``maper_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::

#### MPEPR – Thinness for Height (*Magreza Por Estatura*)

```{r}
mpepr_gam_3 <- mgcv::gam(
  mpepr ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

mpepr_gam_3 |> summary()
```

::: {#tbl-mpepr-gam-3-r2}
```{r}
#| output: asis

mpepr_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mpepr_gam_3` model.
:::

::: {#tbl-mpepr-gam-3-summary-stats}
```{r}
#| output: asis

mpepr_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mpepr_gam_3` model.
:::

::: {#tbl-mpepr-gam-3-coef-stats}
```{r}
#| output: asis

mpepr_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mpepr_gam_3` model.
:::

```{r}
mpepr_gam_3 |> mgcv::gam.check()
```

::: {#fig-mpepr-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = mpepr_gam_3,
    type = 3,
    title = 'Thinness for Height (MPEPR) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of MPEPR'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `mpepr` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``mpepr_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::

#### MAPER & MPEPR – Severe/Moderate Thinness for Height (*Magreza Acentuada/Moderada Para a Estatura*)

```{r}
maper_mpepr_gam_3 <- mgcv::gam(
  maper_mpepr ~ s(spei_12m) + gdp_per_capita + year,
  data = dplyr::mutate(data, year = factor(year, ordered = FALSE)),
  family = mgcv::betar(link = 'logit')
)
```

```{r}
#| code-fold: false

maper_mpepr_gam_3 |> summary()
```

::: {#tbl-maper-mpepr-gam-3-r2}
```{r}
#| output: asis

maper_mpepr_gam_3 |>
  summarise_r2(
    dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`maper_mpepr_gam_3` model.
:::

::: {#tbl-maper-mpepr-gam-3-summary-stats}
```{r}
#| output: asis

maper_mpepr_gam_3 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `maper_mpepr_gam_3` model.
:::

::: {#tbl-maper-mpepr-gam-3-coef-stats}
```{r}
#| output: asis

maper_mpepr_gam_3 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_mpepr_gam_3` model.
:::

```{r}
maper_mpepr_gam_3 |> mgcv::gam.check()
```

::: {#fig-maper-mpepr-gam-3-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = factor(year, ordered = FALSE)) |>
  plot_gam(
    model = maper_mpepr_gam_3,
    type = 3,
    title = 'Severe/Moderate Thinness for Height (MAPER & MPEPR) versus \n Standardised Precipitation Evapotranspiration Index (12 months)',
    x_label = 'Standardised Precipitation Evapotranspiration Index (12 months)',
    y_label = 'Predicted probability of MAPER & MPEPR'
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of `maper_mpepr` as a function of the Standardized Precipitation Evapotranspiration Index (SPEI) (12 months) for the ``maper_mpepr_gam_3`` model. The shaded area represents the 95% prediction confidence interval, with all other variables except SPEI held constant at their mean values.
:::
::::
