:::: {.panel-tabset}
#### MBEPR – Very Short Stature for Age (*Muito Baixa Estatura Para a Idade*)

```{r}
mbepr_gam_2_by_misfs <-
  data |>
  gam_misfs(mbepr ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(mbepr_gam_2_by_misfs)
```

::: {#tbl-mbepr-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

mbepr_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_gam_2_by_misfs` model.
:::

::: {#fig-mbepr-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = mbepr_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MBEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MBEPR (Very Short Stature for Age (*Muito Baixa Estatura Para a Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mbepr_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### BEIPR – Short Stature for Age (*Baixa Estatura Para Idade*)

```{r}
beipr_gam_2_by_misfs <-
  data |>
  gam_misfs(beipr ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(beipr_gam_2_by_misfs)
```

::: {#tbl-beipr-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

beipr_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `beipr_gam_2_by_misfs` model.
:::

::: {#fig-beipr-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = beipr_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of BEIPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of BEIPR (Short Stature for Age (*Baixa Estatura Para Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `beipr_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MBEPR & BEIPR – Very Short/Short Stature for Age (*Muito Baixa/Baixa Estatura Para Idade*)

```{r}
mbepr_beipr_gam_2_by_misfs <-
  data |>
  gam_misfs(mbepr_beipr ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(mbepr_beipr_gam_2_by_misfs)
```

::: {#tbl-mbepr-beipr-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

mbepr_beipr_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_beipr_gam_2_by_misfs` model.
:::

::: {#fig-mbepr-beipr-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = mbepr_beipr_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MBEPR & BEIPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MBEPR & BEIPR (Very Short/Short Stature for Age (*Muito Baixa/Baixa Estatura Para Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mbepr_beipr_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MAPER – Severe Thinness for Height (*Magreza Acentuada Para a Estatura*)

```{r}
maper_gam_2_by_misfs <-
  data |>
  gam_misfs(maper ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(maper_gam_2_by_misfs)
```

::: {#tbl-maper-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

maper_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_gam_2_by_misfs` model.
:::

::: {#fig-maper-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = maper_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MAPER"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MAPER (Severe Thinness for Height (*Magreza Acentuada Para a Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `maper_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MPEPR – Thinness for Height (*Magreza Por Estatura*)

```{r}
mpepr_gam_2_by_misfs <-
  data |>
  gam_misfs(mpepr ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(mpepr_gam_2_by_misfs)
```

::: {#tbl-mpepr-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

mpepr_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mpepr_gam_2_by_misfs` model.
:::

::: {#fig-mpepr-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = mpepr_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MPEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MPEPR (Thinness for Height (*Magreza Por Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mpepr_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MAPER & MPEPR – Severe/Moderate Thinness for Height (*Magreza Acentuada/Moderada Para a Estatura*)

```{r}
maper_mpepr_gam_2_by_misfs <-
  data |>
  gam_misfs(maper_mpepr ~ s(spei_12m) + s(gdp_per_capita) + year)
```

```{r paged.print=FALSE}
#| code-fold: false

data |>
  summarise_gam_misfs(maper_mpepr_gam_2_by_misfs)
```

::: {#tbl-maper-mpepr-gam-2-by-misfs-coef-stats}
```{r}
#| output: asis

maper_mpepr_gam_2_by_misfs |>
  summarise_coefs_misfs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_mpepr_gam_2_by_misfs` model.
:::

::: {#fig-maper-mpepr-gam-2-by-misfs-prediction-versus-spei}
```{r}
data |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam_misfs(
    gam_models = maper_mpepr_gam_2_by_misfs,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MAPER & MPEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MAPER & MPEPR (Severe/Moderate Thinness for Height (*Magreza Acentuada/Moderada Para a Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `maper_mpepr_gam_2_by_misfs` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::
::::
