:::: {.panel-tabset}
#### MBEPR – Very Short Stature for Age (*Muito Baixa Estatura Para a Idade*)

```{r}
mbepr_gam_2 <- mgcv::gam(
  mbepr ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

mbepr_gam_2 |> summary()
```

::: {#tbl-mbepr-gam-2-r2}
```{r}
#| output: asis

mbepr_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mbepr_gam_2` model.
:::

::: {#tbl-mbepr-gam-2-summary-stats}
```{r}
#| output: asis

mbepr_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mbepr_gam_2` model.
:::

::: {#tbl-mbepr-gam-2-coef-stats}
```{r}
#| output: asis

mbepr_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_gam_2` model.
:::

::: {#fig-mbepr-gam-2-effects}
```{r}
plot <- mbepr_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `mbepr_gam_2` model.
:::

::: {#tbl-mbepr-gam-2-concurvity}
```{r}
#| output: asis

mbepr_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `mbepr_gam_2` model terms.
:::

::: {#fig-mbepr-gam-2-diagnostics}
```{r}
mbepr_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `mbepr_gam_2` model.
:::

::: {#fig-mbepr-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = mbepr_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MBEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MBEPR (Very Short Stature for Age (*Muito Baixa Estatura Para a Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mbepr_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### BEIPR – Short Stature for Age (*Baixa Estatura Para Idade*)

```{r}
beipr_gam_2 <- mgcv::gam(
  beipr ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

beipr_gam_2 |> summary()
```

::: {#tbl-beipr-gam-2-r2}
```{r}
#| output: asis

beipr_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`beipr_gam_2` model.
:::

::: {#tbl-beipr-gam-2-summary-stats}
```{r}
#| output: asis

beipr_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `beipr_gam_2` model.
:::

::: {#tbl-beipr-gam-2-coef-stats}
```{r}
#| output: asis

beipr_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `beipr_gam_2` model.
:::

::: {#fig-beipr-gam-2-effects}
```{r}
plot <- beipr_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `beipr_gam_2` model.
:::

::: {#tbl-beipr-gam-2-concurvity}
```{r}
#| output: asis

beipr_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `beipr_gam_2` model terms.
:::

::: {#fig-beipr-gam-2-diagnostics}
```{r}
beipr_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `beipr_gam_2` model.
:::

::: {#fig-beipr-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = beipr_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of BEIPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of BEIPR (Short Stature for Age (*Baixa Estatura Para Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `beipr_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MBEPR & BEIPR – Very Short/Short Stature for Age (*Muito Baixa/Baixa Estatura Para Idade*)

```{r}
mbepr_beipr_gam_2 <- mgcv::gam(
  mbepr_beipr ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

mbepr_beipr_gam_2 |> summary()
```

::: {#tbl-mbepr-beipr-gam-2-r2}
```{r}
#| output: asis

mbepr_beipr_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mbepr_beipr_gam_2` model.
:::

::: {#tbl-mbepr-beipr-gam-2-summary-stats}
```{r}
#| output: asis

mbepr_beipr_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mbepr_beipr_gam_2` model.
:::

::: {#tbl-mbepr-beipr-gam-2-coef-stats}
```{r}
#| output: asis

mbepr_beipr_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mbepr_beipr_gam_2` model.
:::

::: {#fig-mbepr-beipr-gam-2-effects}
```{r}
plot <- mbepr_beipr_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `mbepr_beipr_gam_2` model.
:::

::: {#tbl-mbepr-beipr-gam-2-concurvity}
```{r}
#| output: asis

mbepr_beipr_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `mbepr_beipr_gam_2` model terms.
:::

::: {#fig-mbepr-beipr-gam-2-diagnostics}
```{r}
mbepr_beipr_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `mbepr_beipr_gam_2` model.
:::

::: {#fig-mbepr-beipr-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = mbepr_beipr_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MBEPR & BEIPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MBEPR & BEIPR (Very Short/Short Stature for Age (*Muito Baixa/Baixa Estatura Para Idade*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mbepr_beipr_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MAPER – Severe Thinness for Height (*Magreza Acentuada Para a Estatura*)

```{r}
maper_gam_2 <- mgcv::gam(
  maper ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

maper_gam_2 |> summary()
```

::: {#tbl-maper-gam-2-r2}
```{r}
#| output: asis

maper_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`maper_gam_2` model.
:::

::: {#tbl-maper-gam-2-summary-stats}
```{r}
#| output: asis

maper_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `maper_gam_2` model.
:::

::: {#tbl-maper-gam-2-coef-stats}
```{r}
#| output: asis

maper_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_gam_2` model.
:::

::: {#fig-maper-gam-2-effects}
```{r}
plot <- maper_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `maper_gam_2` model.
:::

::: {#tbl-maper-gam-2-concurvity}
```{r}
#| output: asis

maper_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `maper_gam_2` model terms.
:::

::: {#fig-maper-gam-2-diagnostics}
```{r}
maper_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `maper_gam_2` model.
:::

::: {#fig-maper-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = maper_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MAPER"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MAPER (Severe Thinness for Height (*Magreza Acentuada Para a Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `maper_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MPEPR – Thinness for Height (*Magreza Por Estatura*)

```{r}
mpepr_gam_2 <- mgcv::gam(
  mpepr ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

mpepr_gam_2 |> summary()
```

::: {#tbl-mpepr-gam-2-r2}
```{r}
#| output: asis

mpepr_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`mpepr_gam_2` model.
:::

::: {#tbl-mpepr-gam-2-summary-stats}
```{r}
#| output: asis

mpepr_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `mpepr_gam_2` model.
:::

::: {#tbl-mpepr-gam-2-coef-stats}
```{r}
#| output: asis

mpepr_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `mpepr_gam_2` model.
:::

::: {#fig-mpepr-gam-2-effects}
```{r}
plot <- mpepr_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `mpepr_gam_2` model.
:::

::: {#tbl-mpepr-gam-2-concurvity}
```{r}
#| output: asis

mpepr_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `mpepr_gam_2` model terms.
:::

::: {#fig-mpepr-gam-2-diagnostics}
```{r}
mpepr_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `mpepr_gam_2` model.
:::

::: {#fig-mpepr-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = mpepr_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MPEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MPEPR (Thinness for Height (*Magreza Por Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `mpepr_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::

#### MAPER & MPEPR – Severe/Moderate Thinness for Height (*Magreza Acentuada/Moderada Para a Estatura*)

```{r}
maper_mpepr_gam_2 <- mgcv::gam(
  maper_mpepr ~ s(spei_12m) + s(gini_index) + s(gdp_per_capita) + s(year),
  data = dplyr::mutate(data, year = as.integer(as.character(year))),
  family = mgcv::betar(link = "logit"),
  method = "REML"
)
```

```{r}
#| code-fold: false

maper_mpepr_gam_2 |> summary()
```

::: {#tbl-maper-mpepr-gam-2-r2}
```{r}
#| output: asis

maper_mpepr_gam_2 |>
  summarise_r2(
    dplyr::mutate(data, year = as.integer(as.character(year))) |>
      nrow()
  ) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Confidence interval for the adjusted $\text{R}^{2}$ of the
`maper_mpepr_gam_2` model.
:::

::: {#tbl-maper-mpepr-gam-2-summary-stats}
```{r}
#| output: asis

maper_mpepr_gam_2 |>
  broom::glance() |>
  tidyr::pivot_longer(dplyr::everything()) |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Summary statistics of the `maper_mpepr_gam_2` model.
:::

::: {#tbl-maper-mpepr-gam-2-coef-stats}
```{r}
#| output: asis

maper_mpepr_gam_2 |>
  summarise_coefs() |>
  md_named_tibble()
```

[Source: Created by the authors.]{.legend}

Value of the coefficients in the `maper_mpepr_gam_2` model.
:::

::: {#fig-maper-mpepr-gam-2-effects}
```{r}
plot <- maper_mpepr_gam_2 |>  mgcViz::getViz() |> plot(allTerms = TRUE)

for(i in plot$plots) print(i)
```

[Source: Created by the authors.]{.legend}

Effects of each term in the `maper_mpepr_gam_2` model.
:::

::: {#tbl-maper-mpepr-gam-2-concurvity}
```{r}
#| output: asis

maper_mpepr_gam_2 |>
  mgcv::concurvity(TRUE) |>
  as.data.frame() |>
  pal::pipe_table(label = NA, digits = 10) |>
  pal::cat_lines()
```

[Source: Created by the authors.]{.legend}

Concurvity measures of the `maper_mpepr_gam_2` model terms.
:::

::: {#fig-maper-mpepr-gam-2-diagnostics}
```{r}
maper_mpepr_gam_2 |> mgcViz::getViz() |> mgcViz::check.gamViz()
```

[Source: Created by the authors.]{.legend}

Diagnostics for the `maper_mpepr_gam_2` model.
:::

::: {#fig-maper-mpepr-gam-2-prediction-versus-spei}
```{r}
dplyr::mutate(data, year = as.integer(as.character(year))) |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::matches("^year$"),
      .fns = ~ .x |> as.character() |> as.numeric()
    )
  ) |>
  plot_gam(
    model = maper_mpepr_gam_2,
    type = 2,
    x_label = "Standardised Precipitation Evapotranspiration Index (12 months)",
    y_label = "Predicted probability of MAPER & MPEPR"
  )
```

[Source: Created by the authors.]{.legend}

Predicted probability of MAPER & MPEPR (Severe/Moderate Thinness for Height (*Magreza Acentuada/Moderada Para a Estatura*)) as a function of the smoothed 12-month Standardized Precipitation Evapotranspiration Index (SPEI), based on the `maper_mpepr_gam_2` model. All other variables are held constant at their mean values except SPEI. Shaded areas indicates the pointwise 95% prediction confidence interval, while the faded dots in the background represent the observed data.
:::
::::
