---
title: "analise_sisvan_tempo"
author: "Arthur R Magalhaes"
date: "2025-01-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("./")
PIB_dos_Municípios_base_de_dados_2010_2021 <- read_excel("desktop-tutorial/PIB dos Municípios - base de dados 2010-2021.xlsx", col_types = c("numeric", "numeric", "text", 
      "numeric", "text", "text", "numeric", 
      "text", "text", "numeric", "text", 
      "numeric", "text", "numeric", "text", 
      "text", "numeric", "text", "text", 
      "numeric", "text", "text", "numeric", 
      "text", "text", "text", "numeric", 
      "text", "text", "text", "text", "text", 
      "numeric", "numeric", "numeric", 
      "numeric", "numeric", "numeric", 
      "numeric", "numeric", "text", "text", 
      "text"))
View(PIB_dos_Municípios_base_de_dados_2010_2021)
pib<-PIB_dos_Municípios_base_de_dados_2010_2021

```



```{r}
names(pib)
```

```{r}
# Select the desired columns
pib_selected <- pib[, c("Ano", "Código do Município", "Produto Interno Bruto per capita, \r\na preços correntes\r\n(R$ 1,00)")]

# View the new dataset
head(pib_selected)
# Rename the selected columns for convenience
colnames(pib_selected) <- c("Ano", "Codigo_Municipio", "PIB_per_capita")

# View the new dataset with renamed columns
head(pib_selected)
```

```{r}
data<-read.csv("Banco_dados_malnutritio_clima.csv")
View(data)

```


```{r}
# Rename the column in `pib_selected` for consistency
colnames(pib_selected)[colnames(pib_selected) == "Codigo_Municipio"] <- "code_muni"


# Ensure stringr is loaded
library(stringr)

# Remove the last character from code_muni in pib_selected
pib_selected$code_muni <- str_sub(pib_selected$code_muni, end = -2)

# Convert to integer to match the format in 'data'
pib_selected$code_muni <- as.integer(pib_selected$code_muni)

# Check the updated structure
str(pib_selected)
```
Merge the datasets by 'code_muni' and 'Ano'
```{r}
data$code_muni <- trimws(data$code_muni)
pib_selected$code_muni <- trimws(pib_selected$code_muni)





pib_selected$code_muni <- as.integer(pib_selected$code_muni)
pib_selected$Ano <- as.integer(pib_selected$Ano)
# Merge the datasets by 'code_muni' and 'Ano'
merged_data <- merge(data, pib_selected, by = c("code_muni", "Ano"))

# View the merged dataset
head(merged_data)


```
```{r}
setwd
spei <- read.csv("./merge sisvan extreme events/spei_Extreme_drought_event_municipality_year2.csv")
str(spei)
names(spei)
```

```{r}
# Load necessary libraries
library(dplyr)
library(tidyr)

# Step 1: Select relevant columns
selected_data <- spei %>%
  select(code_muni, starts_with("SPEI_12m_20"))

# Step 2: Reshape the dataset into long format
melted_data <- selected_data %>%
  pivot_longer(
    cols = starts_with("SPEI_12m_20"),  # Columns to melt
    names_to = "Ano",                   # New column for years
    values_to = "SPEI_12m"              # Values from the original columns
  )

# Step 3: Extract the year from the column names
melted_data <- melted_data %>%
  mutate(Ano = gsub("SPEI_12m_", "", Ano))  # Remove "SPEI_12m_" prefix to get the year

# View the result
head(melted_data)
write.csv(melted_data, file="test_spei.csv")


```

```{r}
# Step 4: Remove the last character from `code_muni`
melted_data <- melted_data |> 
  mutate(code_muni = substr(code_muni, 1, nchar(as.character(code_muni)) - 1),
       Ano = as.integer(Ano)  
         )



melted_data <- melted_data %>%
  mutate(code_muni = as.character(code_muni))
merged_data <- merged_data %>%
  mutate(code_muni = as.character(code_muni))
# Ensure `Ano` columns are integers
melted_data <- melted_data %>%
  mutate(Ano = as.integer(Ano))
merged_data <- merged_data %>%
  mutate(Ano = as.integer(Ano))
head(melted_data)
head(merged_data)

# Check for mismatches in `code_muni` formatting
all_equal(merged_data$code_muni, melted_data$code_muni)

# Check for mismatches in `Ano` values
unique(merged_data$Ano)
unique(melted_data$Ano)





# Step 5: Perform the left join
final_data <- left_join(merged_data, melted_data, by = c("Ano", "code_muni"))

# View the merged data
head(final_data)
write.csv(final_data, file="merged_data_spei_new_2025.csv")

```
#Check for muncipalities with minimum 5% cover from sisvan
```{r}
smaller<- sum(final_data$COBRS < 0.05, na.rm = TRUE)
count<- sum(final_data$COBRS > 1, na.rm = TRUE)

# Filter rows where COBRS > 1
filtered_data <- final_data[final_data$COBRS > 1, ]

# Alternatively, using dplyr
library(dplyr)
filtered_data <- final_data %>% filter(COBRS > 1)

write.csv(filtered_data, file="data_above_100.csv")


# Print the result
cat("Number of values greater than 1 in COBRS:", smaller, "\n")


#remove from data rows where cover from sisvan are smaller than 5%
final_data <- final_data[final_data$COBRS >= 0.05, ]

```
##GLMM GERAL
MBEPR - Muito baixa estatura pra Idade
```{r}
library(lme4)
library(glmmTMB)

MBEPR_model <- glmmTMB(
  MBEPR ~ SPEI_12m + PIB_per_capita + (1 | Ano),
  data = final_data,
  family = betabinomial(link = "logit"),
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)



```

```{r}
overdispersion_test <- sum(residuals(MBEPR_model, type = "pearson")^2) / MBEPR_model$df.residual
cat("Overdispersion statistic:", overdispersion_test, "\n")
if (overdispersion_test > 1.5) {
  cat("There might still be overdispersion in the model.\n")
}
# Residuals vs. Fitted Values
plot(MBEPR_model$fitted.values, residuals(MBEPR_model, type = "pearson"),
     xlab = "Fitted Values", ylab = "Pearson Residuals",
     main = "Residuals vs. Fitted")+
abline(h = 0, col = "red")

```

```{r}
library(ggplot2)

ggplot(final_data, aes(x = SPEI_12m, y = MBEPR)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE, color = "blue") +
  labs(
    x = "SPEI (12 months)",
    y = "Probability of MBEPR",
    title = "Relationship between SPEI_12m and MBEPR"
  ) +
  theme_minimal()
``` 
```{r}

library(ggplot2)

ggplot(final_data, aes(x = PIB_per_capita, y = MBEPR)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE, color = "blue") +
  labs(
    x = "income per capta",
    y = "Low stature for age",
    title = "Relationship between Income (per capta) and MBEPR"
  ) +
  theme_minimal()
``` 


BEIPR- Baixa estatura para idade
```{r}
BEIPR_model <- glmmTMB(
  BEIPR ~ SPEI_12m * PIB_per_capita + (1 | Ano),
  data = final_data,
  family = betabinomial(link = "logit")
)
summary(MBEPR_model)


```
MAPER - Magreza acentuada para estatura
```{r}

maper_model <- glm(
  MAPER ~ SPEI_12m * PIB_per_capita,
  data = final_data,
  family = quasibinomial(link = "logit")
)

summary(maper_model)

```
MPEPR = Magreza Por Estatura
```{r}

mpepr_model <- glm(
  MPEPR ~ SPEI_12m * PIB_per_capita,
  data = final_data,
  family = quasibinomial(link = "logit")
)

summary(mpepr_model)
```


##GAMM = generalized additive model mixed effects

#RUN GAMM
 your proportions include exact zeros or ones, you'll need to adjust the data slightly because the beta distribution cannot handle those extremes. You can "nudge" the values slightly, e.g., using:
```{r}

library(mgcv)
final_data$MBEPR <- pmax(0.0001, pmin(0.9999, final_data$MBEPR))

MBEPR_model_gamm <- gam(MBEPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"), 
data = final_data,
  family = betar(link = "logit")
)

summary(MBEPR_model_gamm)



```

```{r}
# Visualize the smooth term for SPEI_12m
plot(MBEPR_model_gamm, pages = 1)
mean(coef(MBEPR_model_gamm))
mean(coef(MBEPR_model_gamm)[grep("s\\(SPEI_12m\\)", names(coef(MBEPR_model_gamm)))])
```

```{r}
library(ggplot2)
library(mgcv)

# Generate a data frame for predictions
# Create a sequence of SPEI_12m values for the plot
new_data <- data.frame(
  SPEI_12m = seq(min(final_data$SPEI_12m, na.rm = TRUE), 
                 max(final_data$SPEI_12m, na.rm = TRUE), 
                 length.out = 200),
  PIB_per_capita = mean(final_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
  Ano = mean(final_data$Ano, na.rm = TRUE) # Keep Ano constant
)

# Add predicted values and confidence intervals
new_data$pred <- predict(MBEPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$fit
new_data$se <- predict(MBEPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$se.fit

# Transform to the response scale if needed (depends on the link function used in the model)
new_data$pred_response <- plogis(new_data$pred) # For beta regression (logit link)
new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)

# Plot the smooth term
ggplot(new_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  labs(
    title = "Estatura Muito baixa para idade e Índice de Precipitação - Evapotranspiração (Índice de Seca)",
    x = "SPEI_12m",
    y = "Predicted MBEPR"
  ) + scale_x_reverse() +  # Invert the X-axis
  theme_minimal()

``` 


#BEIPR - Baixa Estatura para Idade
```{r}
library(mgcv)
final_data$BEIPR  <- pmax(0.0001, pmin(0.9999, final_data$BEIPR ))

BEIPR_model_gamm <- gam(BEIPR  ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"), 
data = final_data,
  family = betar(link = "logit")
)

summary(BEIPR_model_gamm)

```


```{r}
# Visualize the smooth term for SPEI_12m
plot(BEIPR_model_gamm, pages = 1)
mean(coef(BEIPR_model_gamm))
mean(coef(BEIPR_model_gamm)[grep("s\\(SPEI_12m\\)", names(coef(BEIPR_model_gamm)))])
```

```{r}
library(ggplot2)
library(mgcv)

# Generate a data frame for predictions
# Create a sequence of SPEI_12m values for the plot
new_data <- data.frame(
  SPEI_12m = seq(min(final_data$SPEI_12m, na.rm = TRUE), 
                 max(final_data$SPEI_12m, na.rm = TRUE), 
                 length.out = 200),
  PIB_per_capita = mean(final_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
  Ano = mean(final_data$Ano, na.rm = TRUE) # Keep Ano constant
)

# Add predicted values and confidence intervals
new_data$pred <- predict(BEIPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$fit
new_data$se <- predict(BEIPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$se.fit

# Transform to the response scale if needed (depends on the link function used in the model)
new_data$pred_response <- plogis(new_data$pred) # For beta regression (logit link)
new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)

# Plot the smooth term
ggplot(new_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  labs(
    title = "Baixa Estatura para Idade e Índice de Precipitação - Evapotranspiração (Índice de Seca) ",
    x = "SPEI_12m",
    y = "Predicted BEIPR"
  ) + scale_x_reverse() +  # Invert the X-axis
  theme_minimal()

```


##MAPER - Magreza Acentuada por Estatura

```{r}
library(mgcv)
final_data$MAPER  <- pmax(0.0001, pmin(0.9999, final_data$MAPER ))

MAPER_model_gamm <- gam(MAPER  ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"), 
data = final_data,
  family = betar(link = "logit")
)

summary(MAPER_model_gamm)
```

```{r}
# Visualize the smooth term for SPEI_12m
plot(MAPER_model_gamm, pages = 1)
mean(coef(MAPER_model_gamm))
mean(coef(MAPER_model_gamm)[grep("s\\(SPEI_12m\\)", names(coef(MAPER_model_gamm)))])
```

```{r}
library(ggplot2)
library(mgcv)

# Generate a data frame for predictions
# Create a sequence of SPEI_12m values for the plot
new_data <- data.frame(
  SPEI_12m = seq(min(final_data$SPEI_12m, na.rm = TRUE), 
                 max(final_data$SPEI_12m, na.rm = TRUE), 
                 length.out = 200),
  PIB_per_capita = mean(final_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
  Ano = mean(final_data$Ano, na.rm = TRUE) # Keep Ano constant
)

# Add predicted values and confidence intervals
new_data$pred <- predict(MAPER_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$fit
new_data$se <- predict(MAPER_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$se.fit

# Transform to the response scale if needed (depends on the link function used in the model)
new_data$pred_response <- plogis(new_data$pred) # For beta regression (logit link)
new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)

# Plot the smooth term
ggplot(new_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  labs(
    title = "Magreza acentuada e Índice de Precipitação - Evapotranspiração (Índice de Seca)",
    x = "SPEI_12m",
    y = "Predicted MAPER"
  ) + scale_x_reverse() +  # Invert the X-axis
  theme_minimal()
```

```{r}
library(mgcv)
final_data$MPEPR  <- pmax(0.0001, pmin(0.9999, final_data$MPEPR ))

MPEPR_model_gamm <- gam(MPEPR  ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"), 
data = final_data,
  family = betar(link = "logit")
)

summary(MPEPR_model_gamm)
```

```{r}
# Visualize the smooth term for SPEI_12m
plot(MPEPR_model_gamm, pages = 1)
mean(coef(MPEPR_model_gamm))
mean(coef(MPEPR_model_gamm)[grep("s\\(SPEI_12m\\)", names(coef(MPEPR_model_gamm)))])
```
##MPEPR - Magreza por estatura -  geral

```{r}
library(ggplot2)
library(mgcv)

# Generate a data frame for predictions
# Create a sequence of SPEI_12m values for the plot
new_data <- data.frame(
  SPEI_12m = seq(min(final_data$SPEI_12m, na.rm = TRUE), 
                 max(final_data$SPEI_12m, na.rm = TRUE), 
                 length.out = 200),
  PIB_per_capita = mean(final_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
  Ano = mean(final_data$Ano, na.rm = TRUE) # Keep Ano constant
)

# Add predicted values and confidence intervals
new_data$pred <- predict(MPEPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$fit
new_data$se <- predict(MPEPR_model_gamm, newdata = new_data, type = "link", se.fit = TRUE)$se.fit

# Transform to the response scale if needed (depends on the link function used in the model)
new_data$pred_response <- plogis(new_data$pred) # For beta regression (logit link)
new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)

# Plot the smooth term
ggplot(new_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  labs(
    title = "Magreza por estatura e Índice de Precipitação - Evapotranspiração (Índice de Seca)",
    x = "SPEI_12m",
    y = "Predicted MPEPR"
  ) + scale_x_reverse() +  # Invert the X-axis
  theme_minimal()

```


#model check
```{r}
gam.check(MBEPR_model_gamm)
gam.check(BEIPR_model_gamm)
gam.check(MAPER_model_gamm)
gam.check(MPEPR_model_gamm)

```
##analise por misfs

```{r}
# List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MBEPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))

```

```{r}
# List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    BEIPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models))
mean(coef(gamm_models)[grep("s\\(SPEI_12m\\)", names(coef(gamm_models)))])

```

```{r}

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MAPER ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}


```


```{r}
# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MPEPR  ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
```

```{r}

```



```{r}
library(ggplot2)
library(mgcv)
library(dplyr)

# List of MISFS categories
categories <- c("A", "B", "C", "D")

# Initialize an empty data frame to store predictions
prediction_data <- data.frame()

# Loop through each category to fit models and generate predictions
for (category in categories) {
  # Subset data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MBEPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Create a sequence of SPEI_12m values for predictions
  new_data <- data.frame(
    SPEI_12m = seq(
      min(subset_data$SPEI_12m, na.rm = TRUE), 
      max(subset_data$SPEI_12m, na.rm = TRUE), 
      length.out = 200
    ),
    PIB_per_capita = mean(subset_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
    Ano = mean(subset_data$Ano, na.rm = TRUE) # Keep Ano constant
  )
  
  # Add predictions and confidence intervals
  new_data$pred <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$fit
  new_data$se <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$se.fit
  new_data$pred_response <- plogis(new_data$pred) # Transform predictions to response scale
  new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
  new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)
  
  # Add a column for the category
  new_data$MISFS <- category
  
  # Combine predictions into the master data frame
  prediction_data <- rbind(prediction_data, new_data)
}

# Plot the smooth term with facets for each MISFS category
ggplot(prediction_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  facet_wrap(~MISFS, scales = "free_x") +
  scale_x_reverse() +
  labs(
    title = "Estatura Muito Baixa para idade e Indice Precipitação - Evapotranspiração por MISFs",
    x = "SPEI_12m",
    y = "Predicted MBEPR"
  ) +
  theme_minimal()
```



```{r}
# List of MISFS categories
categories <- c("A", "B", "C", "D")

# Initialize an empty data frame to store predictions
prediction_data <- data.frame()

# Loop through each category to fit models and generate predictions
for (category in categories) {
  # Subset data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    BEIPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Create a sequence of SPEI_12m values for predictions
  new_data <- data.frame(
    SPEI_12m = seq(
      min(subset_data$SPEI_12m, na.rm = TRUE), 
      max(subset_data$SPEI_12m, na.rm = TRUE), 
      length.out = 200
    ),
    PIB_per_capita = mean(subset_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
    Ano = mean(subset_data$Ano, na.rm = TRUE) # Keep Ano constant
  )
  
  # Add predictions and confidence intervals
  new_data$pred <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$fit
  new_data$se <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$se.fit
  new_data$pred_response <- plogis(new_data$pred) # Transform predictions to response scale
  new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
  new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)
  
  # Add a column for the category
  new_data$MISFS <- category
  
  # Combine predictions into the master data frame
  prediction_data <- rbind(prediction_data, new_data)
}

# Plot the smooth term with facets for each MISFS category
ggplot(prediction_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  facet_wrap(~MISFS, scales = "free_x") +
  scale_x_reverse() +
  labs(
    title = "Estatura Baixa para idade e Indice Precipitação - Evapotranspiração por MISFs",
    x = "SPEI_12m",
    y = "Predicted BEIPR"
  ) +
  theme_minimal()

```


```{r}
# List of MISFS categories
categories <- c("A", "B", "C", "D")

# Initialize an empty data frame to store predictions
prediction_data <- data.frame()

# Loop through each category to fit models and generate predictions
for (category in categories) {
  # Subset data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MAPER ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Create a sequence of SPEI_12m values for predictions
  new_data <- data.frame(
    SPEI_12m = seq(
      min(subset_data$SPEI_12m, na.rm = TRUE), 
      max(subset_data$SPEI_12m, na.rm = TRUE), 
      length.out = 200
    ),
    PIB_per_capita = mean(subset_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
    Ano = mean(subset_data$Ano, na.rm = TRUE) # Keep Ano constant
  )
  
  # Add predictions and confidence intervals
  new_data$pred <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$fit
  new_data$se <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$se.fit
  new_data$pred_response <- plogis(new_data$pred) # Transform predictions to response scale
  new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
  new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)
  
  # Add a column for the category
  new_data$MISFS <- category
  
  # Combine predictions into the master data frame
  prediction_data <- rbind(prediction_data, new_data)
}

# Plot the smooth term with facets for each MISFS category
ggplot(prediction_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  facet_wrap(~MISFS, scales = "free_x") +
  scale_x_reverse() +
  labs(
    title = "Magreza Acentuada por Estatura e Indice Precipitação - Evapotranspiração por MISFs",
    x = "SPEI_12m",
    y = "Predicted MAPER"
  ) +
  theme_minimal()



```



```{r}
library(ggplot2)
library(mgcv)
library(dplyr)

# List of MISFS categories
categories <- c("A", "B", "C", "D")

# Initialize an empty data frame to store predictions
prediction_data <- data.frame()

# Loop through each category to fit models and generate predictions
for (category in categories) {
  # Subset data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MPEPR ~ s(SPEI_12m) + PIB_per_capita + s(Ano, bs = "re"),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Create a sequence of SPEI_12m values for predictions
  new_data <- data.frame(
    SPEI_12m = seq(
      min(subset_data$SPEI_12m, na.rm = TRUE), 
      max(subset_data$SPEI_12m, na.rm = TRUE), 
      length.out = 200
    ),
    PIB_per_capita = mean(subset_data$PIB_per_capita, na.rm = TRUE), # Keep PIB constant
    Ano = mean(subset_data$Ano, na.rm = TRUE) # Keep Ano constant
  )
  
  # Add predictions and confidence intervals
  new_data$pred <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$fit
  new_data$se <- predict(model, newdata = new_data, type = "link", se.fit = TRUE)$se.fit
  new_data$pred_response <- plogis(new_data$pred) # Transform predictions to response scale
  new_data$upper <- plogis(new_data$pred + 1.96 * new_data$se)
  new_data$lower <- plogis(new_data$pred - 1.96 * new_data$se)
  
  # Add a column for the category
  new_data$MISFS <- category
  
  # Combine predictions into the master data frame
  prediction_data <- rbind(prediction_data, new_data)
}

# Plot the smooth term with facets for each MISFS category
ggplot(prediction_data, aes(x = SPEI_12m, y = pred_response)) +
  geom_line(color = "blue", size = 1) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "blue") +
  facet_wrap(~MISFS, scales = "free_x") +
  scale_x_reverse() +
  labs(
    title = "Magreza por Estatura e Indice Precipitação - Evapotranspiração por MISFs",
    x = "SPEI_12m",
    y = "Predicted MPEPR "
  ) +
  theme_minimal()



```
## how variables vary around time?
```{r}
## List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MPEPR ~  s(Ano),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))

```


```{r}
library(ggplot2)

# Create the ggplot
ggplot(final_data, aes(x = Ano, y = MBEPR)) +
 geom_point(alpha = 0.1, color = "blue") +  # Add scatter points
  geom_smooth(method = "loess", se = FALSE, color = "red") +  # Add a smooth trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Trend of MBEPR Across Years for Different Socioeconomic Clusters",
    x = "Year",
    y = "Proporção de crianças com Estatura Muito baixa para idade (MBPER)",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
  )

 #Create the ggplot
ggplot(final_data, aes(x = Ano, y = MBEPR)) +
 # geom_point(alpha = 0.5, color = "blue") +  # Add scatter points
  geom_smooth(method = "loess", se = FALSE, color = "red") +  # Add a smooth trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Trend of MBEPR Across Years for Different Socioeconomic Clusters",
    x = "Year",
    y = "Proporção de crianças com Estatura Muito baixa para idade (MBPER)",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
  )


library(ggplot2)

# Create the ggplot
ggplot(final_data, aes(x = Ano, y = MBEPR)) +
  #geom_point(alpha = 0.5, color = "blue") +  # Add scatter points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "red") +  # Add GAM trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Tendencia de Estatura Muito Baixa para idade através dos Anos por MISFS",
    x = "Ano",
    y = "MBEPR",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
  )


```


##Tendencia temporal Baixa estatura para idade (BEIPR)
```{r}
## List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    BEIPR ~  s(Ano),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))
```
```{r}
## List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MAPER ~  s(Ano),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))
```
```{r}

# Create the ggplot
ggplot(final_data, aes(x = Ano, y = BEIPR )) +
  #geom_point(alpha = 0.5, color = "blue") +  # Add scatter points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "red") +  # Add GAM trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Tendencia de Baixa Estatura por Idade através dos anos por MISFS",
    x = "Year",
    y = "BEIPR ",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
  )



```

```{r}
## List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MAPER ~  s(Ano),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))
```


```{r}
# Create the ggplot
ggplot(final_data, aes(x = Ano, y = MAPER )) +
  #geom_point(alpha = 0.5, color = "blue") +  # Add scatter points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "red") +  # Add GAM trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Tendencia de Magreza Acentuada por Estatura através dos Anos por MISFS",
    x = "Year",
    y = "MAPER ",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
  )

```



```{r}
## List of categories in MISFS
categories <- c("A", "B", "C", "D")

# Initialize a list to store models
gamm_models <- list()

# Loop through each category
for (category in categories) {
  # Subset the data for the current category
  subset_data <- subset(final_data, MISF == category)
  
  # Fit the GAM model for the subset
  model <- gam(
    MPEPR ~  s(Ano),
    data = subset_data,
    family = betar(link = "logit")
  )
  
  # Store the model in the list
  gamm_models[[category]] <- model
  
  # Print a summary for the model
  cat("\nSummary for category", category, ":\n")
  print(summary(model))
}
mean(coef(gamm_models[["A"]]))
mean(coef(gamm_models[["B"]]))
mean(coef(gamm_models[["C"]]))
mean(coef(gamm_models[["D"]]))
```

```{r}
# Create the ggplot
ggplot(final_data, aes(x = Ano, y = MPEPR  )) +
  #geom_point(alpha = 0.5, color = "blue") +  # Add scatter points
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), color = "red") +  # Add GAM trend line
  facet_wrap(~ MISF, ncol = 2) +  # Create facets for each MISF category
  labs(
    title = "Tendencia Magreza por Estatura através dos Anos por MISFS",
    x = "Ano",
    y = "MPEPR",
    caption = "Data Source: SISVAN"
  ) +
  theme_minimal() +  # Apply a clean theme
  theme(
    strip.text = element_text(size = 12, face = "bold"),  # Style facet labels
    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels for clarity
)

```

#teste whether temporal tendencies are signifnicant
Mbper first
```{r}
# Create a list to store models
gam_models <- list()

# Loop through each MISF category and fit a GAM model
for (misf_level in unique(final_data$MISF)) {
  # Subset data for the current MISF level
  subset_data <- subset(final_data, MISF == misf_level)
  
  # Fit the GAM model
  gam_model <- gam(MBEPR ~ s(Ano), data = subset_data)
  
  # Store the model in the list
  gam_models[[misf_level]] <- gam_model
}

# Display summaries for each model
for (misf_level in names(gam_models)) {
  cat("\n### GAM Summary for MISF =", misf_level, "###\n")
  print(summary(gam_models[[misf_level]]))
}


```

```{r}
results <- data.frame(
  MISF = character(),
  EDF = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE
)

for (misf_level in names(gam_models)) {
  model_summary <- summary(gam_models[[misf_level]])
  results <- rbind(results, data.frame(
    MISF = misf_level,
    EDF = model_summary$s.table[1, "edf"],
    p_value = model_summary$s.table[1, "p-value"]
  ))
}

print(results)

```


```{r}
 #Create a list to store models
gam_models <- list()

# Loop through each MISF category and fit a GAM model
for (misf_level in unique(final_data$MISF)) {
  # Subset data for the current MISF level
  subset_data <- subset(final_data, MISF == misf_level)
  
  # Fit the GAM model
  gam_model <- gam(BEIPR ~ s(Ano), data = subset_data)
  
  # Store the model in the list
  gam_models[[misf_level]] <- gam_model
}

# Display summaries for each model
for (misf_level in names(gam_models)) {
  cat("\n### GAM Summary for MISF =", misf_level, "###\n")
  print(summary(gam_models[[misf_level]]))
}
results <- data.frame(
  MISF = character(),
  EDF = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE
)

for (misf_level in names(gam_models)) {
  model_summary <- summary(gam_models[[misf_level]])
  results <- rbind(results, data.frame(
    MISF = misf_level,
    EDF = model_summary$s.table[1, "edf"],
    p_value = model_summary$s.table[1, "p-value"]
  ))
}

print(results)
```

```{r}
 #Create a list to store models
gam_models <- list()

# Loop through each MISF category and fit a GAM model
for (misf_level in unique(final_data$MISF)) {
  # Subset data for the current MISF level
  subset_data <- subset(final_data, MISF == misf_level)
  
  # Fit the GAM model
  gam_model <- gam(MAPER ~ s(Ano), data = subset_data)
  
  # Store the model in the list
  gam_models[[misf_level]] <- gam_model
}

# Display summaries for each model
for (misf_level in names(gam_models)) {
  cat("\n### GAM Summary for MISF =", misf_level, "###\n")
  print(summary(gam_models[[misf_level]]))
}

results <- data.frame(
  MISF = character(),
  EDF = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE
)

for (misf_level in names(gam_models)) {
  model_summary <- summary(gam_models[[misf_level]])
  results <- rbind(results, data.frame(
    MISF = misf_level,
    EDF = model_summary$s.table[1, "edf"],
    p_value = model_summary$s.table[1, "p-value"]
  ))
}

print(results)

```


```{r}
 #Create a list to store models
gam_models <- list()

# Loop through each MISF category and fit a GAM model
for (misf_level in unique(final_data$MISF)) {
  # Subset data for the current MISF level
  subset_data <- subset(final_data, MISF == misf_level)
  
  # Fit the GAM model
  gam_model <- gam(MPEPR ~ s(Ano), data = subset_data)
  
  # Store the model in the list
  gam_models[[misf_level]] <- gam_model
}

# Display summaries for each model
for (misf_level in names(gam_models)) {
  cat("\n### GAM Summary for MISF =", misf_level, "###\n")
  print(summary(gam_models[[misf_level]]))
}

results <- data.frame(
  MISF = character(),
  EDF = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE
)

for (misf_level in names(gam_models)) {
  model_summary <- summary(gam_models[[misf_level]])
  results <- rbind(results, data.frame(
    MISF = misf_level,
    EDF = model_summary$s.table[1, "edf"],
    p_value = model_summary$s.table[1, "p-value"]
  ))
}

print(results)

```